---
title: "The RosaMatDec Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The RosaMatDec Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(RosaMatDec)
```

# Introduction

This package creates many items from a 3x2 matrix for OU course MATH5793. There is also an S3 method for plotting the data matrix in 2D.

# Example `myMatdec()`

First, we need a matrix. So let $\mathbf{M}$ be a $3x2$ matrix such as

$$
\mathbf{M} = 
  \begin{bmatrix}
    4 & 1 \\
    -1 & 3 \\
    3 & 5 \\
  \end{bmatrix}
$$

Define the matrix in `R`

```{r}
M <- matrix(c(4,1,-1,3,3,5), nrow = 3, ncol = 2, byrow = TRUE)
M
```

```{r}
m <- myMatdec(X = M)
m
```

The following explains each item:

  - $X$ - The original matrix
  - $xBar$ - The mean vector
  - $x1, \ x2, \ x3$ - Transverse vectors of the rows
  - $y1 \ \& \ y2$ - Vectors of the columns
  - $d1 \ \& \ d2$ - Deviation vectors
  - $Ld1 \ \& \ Ld2$ - Length of the deviation vectors
  - $s11, \ s22, \ \& \ s12$ - Variances of $d1$ and $d2$, respectively, and the covariance.
  - $r12$ - Correlation coefficient 
  - $Theta$ - angle between the deviation vectors

# Example `myMatdec.plot2d()`

The package also contains an `S3 method` for plotting the original data matrix in $2D$.

```{r, fig.align='center', fig.width=7, fig.height=5}
myMatdec.plot2d(X = M)
```


